---
title: "Hypothesis Testing"
author: "Enqun Wang (EW), Yiyan Zhou (YZ)"
date: "April 26, 2016"
output: html_document
---



#### Input the data

```{r message=FALSE}
setwd("/Users/zhouyiyan/Documents/STAA568 Topics in Industrial Organizational Statistics/DMAIC/Case Study/3-Analyze")

require(dplyr)

df = data.frame(read.csv("data.csv", header = T)[-c(1:4),-c(2:3)])
head(df)
```


According to the exploratory data analysis, we decide to first elect variables as follows,

- Product Factor:

1. Rate of Return
2. Term
3. TZD Account

- Promotion Factor:

1. LB Received
2. LB Used

- Platform Factor:

1. Balance
2. Capital Inflow

- Market Factor:

1. R.007


#### Rate of Return

```{r}
chisq.test(df$Rate.of.Return, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the rate of return.



#### Term

```{r}
chisq.test(df$Term, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the term.


#### TZD Account

```{r}
chisq.test(df$TZD.Account, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the TZD Account.


#### LB Received

```{r}
chisq.test(df$LB.Received, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the LB Received.


#### LB Used

```{r}
chisq.test(df$LB.Used, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the LB Used.


#### Balance

```{r}
chisq.test(df$Balance, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the balance.


#### Capital Inflow

```{r}
chisq.test(df$Capital.Inflow, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the Capital Inflow.



#### R.007

```{r}
chisq.test(df$R.007, df$Increase.Rate.5Day)
```

The p-value of the test is less than 0.05, and we reject the null hypothesis and conclude that the 5-day increase rate is not independent of the R.007.